Fair Queuing Aware Congestion Control

### 2022-06-23 tex/paper.tex
Add reference

The core concept of our approach, which we call \textbf{\textit{Tonopah}}, is that a network flow is separated into \textbf{two subflows}. 
\textbf{Alternatingly}, one flow sends more (\textbf{dominant subflow}), while the other one sends less (\textbf{non-dominant subflow}). 
After a certain time interval the dominant subflow becomes the non-dominant one and vice versa. 
When the total sending rate reaches the link capacity and fair queuing is present, 
\textbf{fair queuing} is going to \textbf{limit} the throughput of the \textbf{dominant subflow} (\autoref{fig:illustration_fq}). 
This can be measured by observing the \textit{delivery rate}
\footnote{The delivery rate (a concept popularized by BBR \cite{cardwell_bbr_2016}) can be measured by observing the rate at which acknowledgement packets are sent back to the sender by the receiver.
If the sender sends more than the link capacity, the delivery rate is never going to exceed the link capacity since the receiver cannot receive packets faster than the link capacity allows. 
}
of both subflows. If there is no fair queuing, the subflow which sends more also achieves higher throughput (\autoref{fig:illustration_no_fq}). 
In this case, Tonopah doesn't behave different from a network flow which doesn't have fair queuing detection. 
This can be a potential advantage which a Tonopah-enabled congestion control can have over other congestion control algorithms such as BBR, which has been shown to be unfair to other flows sometimes \cite{ware_modeling_2019}.

>>>>

The core concept of our approach, which we call \textbf{\textit{Tonopah}}, is that a network flow is separated into \textbf{two subflows}. 
\textbf{Alternatingly}, one flow sends more (\textbf{dominant subflow}), while the other one sends less (\textbf{non-dominant subflow}). 
After a certain time interval the dominant subflow becomes the non-dominant one and vice versa. 
When the total sending rate reaches the link capacity and fair queuing is present, 
\textbf{fair queuing} is going to \textbf{limit} the throughput of the \textbf{dominant subflow} (\autoref{fig:illustration_fq}). 
This can be measured by observing the \textit{delivery rate}
\footnote{The delivery rate (a concept popularized by BBR \cite{cardwell_bbr_2016}) can be measured by observing the rate at which acknowledgement packets are sent back to the sender by the receiver.
If the sender sends more than the link capacity, the delivery rate is never going to exceed the link capacity since the receiver cannot receive packets faster than the link capacity allows. 
}
of both subflows. If there is no fair queuing, the subflow which sends more also achieves higher throughput (\autoref{fig:illustration_no_fq}). 
In this case, Tonopah doesn't behave different from a network flow which doesn't have fair queuing detection. 
This can be a potential advantage which a Tonopah-enabled congestion control can have over other congestion control algorithms such as BBR, which has been shown to be unfair to other flows sometimes \cite{ware_modeling_2019,hock_experimental_2017}.
